Races with hyper3 objects

### 2022-04-16 inst/race3.Rmd
more work on constructors

@@

# The constructors championship

@@

@@

```{r}
pie(mc)
```

>>>>

(takes about 15 minutes to process)

@@

$$
\mathcal{L}(a)=
\frac{a}{2a+2b}\cdot
\frac{b}{ a+2b}\propto\frac{a(1-a)}{2-a}
$$

(see how the likelihood function is actually simpler than for the
complete order statistic).  The evaluate would be $2-\sqrt{2}\simeq
0.586$:

```{r label=maxnonfinishers,cache=TRUE}
o <- ordervec2supp3(c("a","b"),nonfinishers=c("a","b"))
o
maxp(o)
```

# The constructors' championship

@@

Looking at the first column we see that the constructors are Mercedes
("`Merc`"), Red Bull Racing Honda ("`RBRH`"), and so on.  Each
constructor fields two cars in each race.  Looking at the next column,
we see the order statistic for Bahrain (`BHR`).  We see that Mercedes
came first and third, Red Bull came second and fifth, Ferrari sixth
and eighth, and so on.

@@

```{r,label=drawaconstructorpie}
pie(mc)
```

We may test the null of equal strengths:

```{r,label=testequalityconstructor,cache=TRUE}
equalp.test(constructor_2021)
```

and see that there is (very) strong evidence to reject this null.
Further, we may test the hypothesis that the big four (viz Mercedies,
Ferrari, Red Bull Racing Honda, and McLaren-Mercedes) are equal:

```{r,label=testsameconstructor,cache=TRUE}
samep.test(constructor_2021,c("Merc","Ferrari","RBRH","MM")) # ~10 mins
```

and fail to reject that null.
